%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Stylish Curriculum Vitae
% LaTeX Template
% Version 1.0 (18/7/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Stefano (http://stefano.italians.nl/)
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% The main font used in this template, Adobe Garamond Pro, does not 
% come with Windows by default. You will need to download it in
% order to get an output as in the preview PDF. Otherwise, change this 
% font to one that does come with Windows or comment out the font line 
% to use the default LaTeX font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper, oneside, final]{scrartcl} % Paper options using the scrartcl class

\usepackage{scrpage2} % Provides headers and footers configuration
\usepackage{titlesec} % Allows creating custom \section's
\usepackage{marvosym} % Allows the use of symbols
\usepackage{tabularx,colortbl} % Advanced table configurations
\usepackage{fontspec} % Allows font customization
\usepackage[UTF8]{ctex} % Allows chinese support
\usepackage[hidelinks]{hyperref} % Allows highlight url and hyperref
\usepackage{fontawesome} % Allow awesome symbols like faGraduationCap

\defaultfontfeatures{Mapping=tex-text}
\setmainfont{Adobe Garamond Pro} % Main document font

\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule] % Section formatting

\pagestyle{scrheadings} % Print the headers and footers on all pages

\addtolength{\voffset}{-0.5in} % Adjust the vertical offset - less whitespace at the top of the page
\addtolength{\textheight}{3cm} % Adjust the text height - less whitespace at the bottom of the page

\newcommand{\gray}{\rowcolor[gray]{.90}} % Custom highlighting for the work experience and education sections

%----------------------------------------------------------------------------------------
% FOOTER SECTION
%----------------------------------------------------------------------------------------

\renewcommand{\headfont}{\normalfont\rmfamily} % Font settings for footer

\cofoot{
\fontsize{12}{17}\selectfont % Letter spacing and font size

North Renmin Road Number 2999 Building 3 {\large\textperiodcentered} Songjiang {\large\textperiodcentered} Shanghai \\ % Your mailing address
{\Large\Letter} wangxin19930411@163.com \ {\Large\Telefon} (+86) 133-9148-8435 \ 
{\Large\faGithub} github.com/WangXin93% Your email address and phone number
}

%----------------------------------------------------------------------------------------

\begin{document}

\begin{center} % Center everything in the document

%----------------------------------------------------------------------------------------
% HEADER SECTION
%----------------------------------------------------------------------------------------

{\addfontfeature{LetterSpace=20.0}\fontsize{36}{36}\selectfont\scshape Xin Wang} % Your name at the top

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\section{\faInfo\ Introduction}
\begin{flushleft}
I'm a Ph.D candidate in the Textile Institute at Donghua University in Shanghai, China.

My research interests lie at the understanding of fashion images, text descrptions and fashion compatibility and recommendation based on different modalilites of information.
\end{flushleft}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\section{\faUsers\ Researches \& Projects}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Time & \textbf{Aug 2018 --- Mar 2019}\\
\gray Location & \textbf{JD AI Research} \\
\gray Title & \textbf{Outfit Compatibility Prediction and Diagnosis with Multi-Layered Comparison Network (ACM MM19 Under Review)}\\
\gray Tools & \textbf{Python, PyTorch}\\
& Propose to not only predict the compatibility of fashion outfit but also diagnose the incompatible factor in it. Our method features for: (1) learn outfit compatibility from all pairwise similarities. (2) Leverage the feature hierarchy of CNN to provide both low-level and high-level features for prediction and diagnosis. (3) Use gradients to approximate the importance of each input similarity for explanation.
\end{tabularx}

\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Time & \textbf{Oct 2017 --- Jul 2018}\\
\gray Title & \textbf{Fabric Idenfication using Convolutional Neural Network (\href{https://www.polyu.edu.hk/itc/aift2018/}{AIFT2018})}\\
\gray Tools & \textbf{Python, TensorFlow}\\
& Propose to retrieve fabric texture with deep extracted features, which is implemented with a CNN with softmax cross entropy and centor loss. Code: \url{https://github.com/WangXin93/FabricID}
\end{tabularx}

\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Time & \textbf{Mar 2018 --- Jul 2018}\\
\gray Title & \textbf{\href{http://fashionai.alibaba.com/}{FashionAI Global Challenge}}\\
\gray Tools & \textbf{Python, PyTorch}\\
& Recognize 8 fashion attribute with convolutional neural network. We go through the first round and achieve \href{https://tianchi.aliyun.com/competition/rankingList.htm?\&season=0\&raceId=231649\&pageIndex=5}{66th} in the second round. Code: \url{https://github.com/WangXin93/torchfashion}
\end{tabularx}

\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Time & \textbf{Jul 2018}\\
\gray Title & \textbf{\href{https://fashion-challenge.github.io/}{JD AI Fashion-Challenge Style Recognition}}\\
\gray Tools & \textbf{Python, PyTorch}\\
& Multi-labeled prediction of 13 styles of female fashion images. I finetune the threshold of different labels and use {SWA} to improve the performance, finally achieve \href{https://fashion-challenge.github.io/style-rank.html}{4th} place in the competition.
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{\faGraduationCap\ Education}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Time & \textbf{Sep 2015 --- Current}\\
\gray Degree & \textbf{Digital Textile Engineering (Ph.D)}\\
\gray Course & \textbf{Numerical analysis，Computer graphics，Computer vision，Self-educated: \href{https://github.com/WangXin93/CS231n-Spring-2017-Assignment}{CS231n}，\href{https://github.com/WangXin93/CS20SI-my-example}{CS20SI}， \href{https://github.com/WangXin93/machine_learning}{Machine Learning}，\href{https://github.com/WangXin93/My_python_demo}{Python}}\\
\gray University & \textbf{Donghua University} \hfill Shanghai, China\\
%& Extra information about degree
\end{tabularx}

\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Time & \textbf{Sep 2011 --- Jul 2015}\\
\gray Degree & \textbf{Textile Engineering (B.S.)}\\
\gray Courses & \textbf{Advanced mathematics，Linear algebra，Probability theory and mathematical statistics}\\
\gray University & \textbf{Langzhou University of Technology} \hfill Gansu, China\\
%& Extra information about degree
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\section{\faCogs\ Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Language & Intermediate: Python; Basic: C/C++, Bash, Matlab, SQL \\
Deep Learning Framework & TensorFlow, PyTorch \\
Tools & Git, Vim, \LaTeX, Scrapy, Scikit-learn, Sed, Awk
\end{tabular}

%----------------------------------------------------------------------------------------

\end{center}

\end{document}